Division and Slope Factorization of p-Adic Polynomials

### 2016-01-31 polynomials/muldivfact.tex
Tiny change in todo spacing
Title changed
One typo
One typo corrected...

\title{Division and Factorization of p-Adic Polynomials}

@@

\smallskip\noindent 9.\ 
{\bf return} $A_i$

@@

As for the second question, the discussion is similar to the case of 
Newton precision expect that we need a new stop criterium. It is given 
by the following proposition.

>>>>

\title{Division and Slope Factorization of p-Adic Polynomials}

@@

\smallskip\noindent 9.\ 
{\bf return} $A_i + O(\varphi_A)$

@@

As for the second question, the discussion is similar to the case of 
Newton precision expect that we need a new stopping criterion. It is given 
by the following proposition.
